Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-06-16 sas2015/content/background.tex
corrections

Thanks to distributivity, every environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
can be decomposed into its effect on $\top_{\textsf{Env}}$ and on a set of environments $\top_{\textsf{Env}}[d_i\to l]$
that map every element to $\top$ except one ($d_i$):
\[
    t(m)(d_j) = \lambda l. t(\top_{\textsf{Env}})(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\top_{\textsf{Env}}[d_i\to l])(d_j).
\]
The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
appear on the edges of the pointwise representation edges from $\mathbf0$ to each $d_j$ and from
each $d_i$ to each $d_j$.%
\footnote{The IDE paper defines a more complicated but equivalent set of micro-functions
that eliminate some duplication of computation.}
The absence of an edge in the pointwise representation from some $d_i$ to some $d_j$ is
equivalent to an edge with micro-function $\lambda l.\top$.

\begin{example}
    In the exploded supergraph in Figure~\ref{fig:cc_edgefn_example},
    the micro-functions are shown as labels on the graph edges.
    Every edge without an explicit label has the identity as its
    micro-function. The micro-functions on the three edges from
    the node \verb+return secret()+ to the node $\texttt{end}_\texttt{A.foo}$
    together represent the environment transformer 
    $\lambda e.e[r \to \lambda m.\bot \sqcap \lambda m.m]$.

    To eliminate infeasible paths due to correlated calls, we encode the taint
    analysis using environments $\textsf{Env}(D,L)$, where $D$ is the set of
    variables and $L$ is a map from receiver variables to sets of possible
    types. The interpretation of such an environment $e$ is that a given variable
    $v \in D$ may contain a secret value in an execution in which the runtime
    types of the objects pointed to by the receiver variables are in the sets
    specified by $e(v)$.
\end{example}

>>>>

Thanks to distributivity, every environment transformer 
$t : \textsf{Env}(D,L) \to \textsf{Env}(D,L)$
can be decomposed into its effect on $\top_{\textsf{Env}}$ and on a set of environments $\top_{\textsf{Env}}[d_i\to l]$
that map every element to $\top$ except one ($d_i$). Formally,
\[
    t(m)(d_j) = \lambda l. t(\top_{\textsf{Env}})(d_j) \sqcap \bigsqcap_{d_i\in D} \lambda l. t(\top_{\textsf{Env}}[d_i\to l])(d_j).
\]
The functions $\lambda l. \cdots$ in this decomposition are the micro-functions that
appear on the edges of the pointwise representation edges from $\mathbf0$ to each $d_j$ and from
each $d_i$ to each $d_j$.%
\footnote{The IDE paper defines a more complicated but equivalent set of micro-functions
that eliminate some duplication of computation.}
The absence of an edge in the pointwise representation from some $d_i$ to some $d_j$ is
equivalent to an edge with micro-function $\lambda l.\top$.

\begin{example}
    In the exploded supergraph in Figure~\ref{fig:cc_edgefn_example},
    the micro-functions are shown as labels on the graph edges.
    Every edge without an explicit label has the identity as its
    micro-function. The micro-functions on the three edges from
    the node \verb+return secret()+ to the node $\texttt{end}_\texttt{A.foo}$
    together represent the environment transformer 
    $\lambda e.e[\texttt{ret} \to \lambda m.\bot \sqcap \lambda m.m]$.

    To eliminate infeasible paths due to correlated calls, we encode the taint
    analysis using environments $e\in\textsf{Env}(D,L)$, where $D$ is the set of
    variables and $L$ is a map from receiver variables to sets of possible
    types. The interpretation of such an environment $e$ is that a given variable
    $v \in D$ may contain a secret value in an execution in which the runtime
    types of the objects pointed to by the receiver variables are in the sets
    specified by $e(v)$.
\end{example}

### 2015-06-16 sas2015/content/impl.tex
corrections

In the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
an IFDS solution as:
  $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
%is converted to an IFDS result as follows:
%\begin{equation}\label{eq:transEqDef}
  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
%\end{equation}
%
%\otodo{I don't understand this comment. What does it mean?}
%
In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data-flow path is
infeasible. Therefore, an IDE solution $\rho$ computed using
$\transCC_S$ is converted to an IFDS solution as:
$\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}$.

@@

To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
calls.

>>>>

In the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
an IFDS solution as:
  $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
%is converted to an IFDS result as follows:
%\begin{equation}\label{eq:transEqDef}
  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
%\end{equation}
%
%\otodo{I don't understand this comment. What does it mean?}
%
In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data-flow path is
infeasible. Therefore, an IDE solution $\rho$ computed using
$\transCC_S$ is converted to an IFDS solution as
\begin{equation}
	\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.\label{eq:transCcDef}
\end{equation}

@@

To evaluate the practicality of our approach, we applied two variants of the IFDS taint analysis
to the SPEC JVM98 benchmarks: 
\begin{enumerate}[(i)]
	\item an equivalent IDE taint analysis obtained using $\transEq$, and
	\item an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
calls.
\end{enumerate}
The equivalence analysis is there for two reasons: 
\begin{enumerate}[(i)]
	\item  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem; 
	\item (ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis.
\end{enumerate}
We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.

### 2015-06-16 sas2015/content/related.tex
corrections

Our approach superficially resembles, but is orthogonal, to context
sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), whereas we analyze control flow paths.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
in a flow-sensitive setting since a flow-insensitive analysis already
introduces many infeasible control flow paths.

>>>>

Our approach superficially resembles, but is orthogonal to, context
sensitivity, including the CPA algorithm~\cite{Agesen:95} and such variations as object sensitivity~\cite{DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), whereas we analyze control flow paths.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
in a flow-sensitive setting since a flow-insensitive analysis already
introduces many infeasible control flow paths.
